Proportional multi-state multiple-cohort life table model

### 2018-04-17 MSLT/MSLTdoc.Rmd
FInalised compare plots UK
Separate compare plots to another doc

4) Read GBD data
```{r, echo=TRUE}
GBDdata <- read.csv("MSLT/data/UK/englandandgreaterlondon.csv", stringsAsFactors = F)
```

@@

14) Generate graphs to compare GBD data for England and Greater London.

```{r, echo=FALSE}
###TO DO: cubic splines for input rates

#in_data1: GBDEngland
#in_data2: GBDGL

p_sex <- c("male", "female")
p_cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancer", "breast cancer", "tracheal, bronchus, and lung cancer")
p_measure <- c("deaths", "ylds (years lived with disability)", "prevalence", "incidence")

for (sex in p_sex){
  for (cause in p_cause) {
    for (measure in p_measure){

# Exclude breast_cancer for Males
      if (sex == "male" && cause == "breast cancer" || cause == "all causes" && measure == "prevalence" || cause == "all causes" && measure == "incidence"){
        p1 <- NULL

      }
      else {
      p1 <- plot_GBD(in_data1 = GBDEngland, in_data2 = GBDGL, in_sex = sex, in_cause = cause, in_measure = measure)

      }
    }
  }
}

```

FIX GRAPHS TITLES.

>>>>

4) Read GBD data
```{r, echo=TRUE}
GBDdata <- read.csv("data/UK/englandandgreaterlondon.csv", stringsAsFactors = F)
```

@@
